Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Paper/paper-draft-Padgett-Thiam.Rmd
Update paper-draft-Padgett-Thiam.Rmd

This section describes the data sources and the data gathering process.

>>>>

Using the rtweet package and the search_tweet function, we were able to gather sufficient tweets for our project and classified it as pre or post debate. The initial dataset contains a little over 1.3 million tweets which was rich enough to proceed with analysis. After removing irrelevant tweets such as tweets containing "Ukraine", we were left with 1.2 million tweets which we then divided in two groups :pre and post debate. The pre-debate dataset has 226,799 tweets and 998,780 tweets for the post-debate dataset. As expected, there was a lot more tweets after the debate than before. With Twitter having a location column, we wanted to focus our anylysis on certain regions/ states in the U.S., however the location column is an open text and not regulated. We then picked a few states to focus our analysis on.
